---
title: "Vehicle Choice App"
author: "NHartley"
date: "2024-03-02"
output:
  ioslides_presentation:
    css: default
  beamer_presentation:
    css: default
  slidy_presentation:
    default
---

```{css, echo=FALSE}
/* Global font adjustments */
.slides {
  font-size: 14px;
  font-family: 'Helvetica Neue', Arial, sans-serif; /* Change the font globally */
  color: #0056b3; /* Global text color - Dark gray */
}

/* Specific adjustment for the Overview slide elements */
#overview .content {
  font-size: 12px;
  color: #0056b3; /* Change text color specifically for Overview slide content - Blue */
}

/* Change the color for all headings */
.slides h1, .slides h2, .slides h3, .slides h4, .slides h5, .slides h6 {
  color: #007bff; /* Darker blue */
}

/* Optionally, if you want a specific paragraph or element to have a different text color */
.special-text {
  color: #0077cc; /* Slightly lighter blue */
}

/* Reduce the bottom margin of all headers */
.slides h1, .slides h2, .slides h3, .slides h4, .slides h5, .slides h6 {
  margin-bottom: 10px; /* Adjust this value as needed */
}

/* Reduce the top margin of unordered and ordered lists */
.slides ul, .slides ol {
  margin-top: 0px; /* Adjust this value as needed */
}

```


```{r setup, include=FALSE}
# Install and load required packages
required_packages <- c("knitr", "kableExtra", "dplyr", "ggplot2", "gridExtra")

new_packages <- required_packages[!(required_packages %in% installed.packages()[,"Package"])]
if(length(new_packages)) install.packages(new_packages)

library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(gridExtra)

knitr::opts_chunk$set(echo = FALSE)
cat("
<style>
.slides * {
  font-size: 14px !important; /* Smaller font size to fit more content */
}

/* Reduce the bottom margin of all headers */
.slides h1, .slides h2, .slides h3, .slides h4, .slides h5, .slides h6 {
  margin-bottom: 10px; /* Adjust this value as needed */
}

/* Reduce the top margin of unordered and ordered lists */
.slides ul, .slides ol {
  margin-top: 0px; /* Adjust this value as needed */
}
</style>
", file = "styles.css")


```

## OVERVIEW {.smaller}

### INTENT
-   The goal of this app is for users to highlight eligible cars from the mtcars dataset by toggling two variables:
-   Transmission type (manual vs. automatic)
-   Miles per Gallon (mpg)

### INSTRUCTIONS
-   1: Select choice of transmission type with the radio button
-   2: Select mpg threshold using the slider
-   3: Click "Submit"

### DESCRIPTION OF DATA SET
-   The mtcars dataset is a dataset available in R
-   It comprises fuel consumption and 10 aspects of design and performance for 32 vehicles

## MTCARS SUMMARY STATISTICS {.smaller}
```{r echo=FALSE, eval = TRUE}
# Load the mtcars dataset
data(mtcars)

# Displaying summary statistics in two parts
summary_statistics_part1 <- summary(mtcars[,1:6])
summary_statistics_part2 <- summary(mtcars[,7:11])

# Use kable to present these statistics
kable(summary_statistics_part1, format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

kable(summary_statistics_part2, format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

```

## ANALYSIS 1 {.smaller}
```{r plots, echo=FALSE, fig.width=8, fig.height=5}
library(ggplot2)
library(gridExtra)

# Boxplot comparing mpg for manual and automatic transmissions using ggplot2
boxplot_mpg <- ggplot(mtcars, aes(x=factor(am), y=mpg, fill=factor(am))) +
  geom_boxplot() +
  labs(title="MPG Comparison by Transmission Type",
       x="Transmission Type", y="Miles Per Gallon") +
  scale_fill_manual(values=c("pink", "brown"), labels=c("Automatic", "Manual")) +
  theme_minimal() +
  theme(legend.title=element_blank())

# Linear model plot
model <- lm(mpg ~ wt + cyl + as.factor(am), data=mtcars)
mtcars$predicted_mpg <- predict(model)

plot_lm <- ggplot(mtcars, aes(x=mpg, y=predicted_mpg)) +
  geom_point() +
  geom_abline(intercept=0, slope=1, color="brown") +
  labs(title="Observed vs. Fitted MPG (using Weight,\n Cylinders, and Trans. Type)",
       x="Observed MPG", y="Fitted MPG") +
  theme_minimal()

# Combine plots side by side using gridExtra
grid.arrange(boxplot_mpg, plot_lm, ncol=2)

```


## ANALYSIS 2 {.smaller}
```{r additional_plots, echo=FALSE, warning=FALSE, fig.width=8, fig.height=5}
# Histogram of Cylinders vs. Weight
histogram <- ggplot(mtcars, aes(x = cyl, y = wt)) +
  geom_histogram(stat = "identity", fill = "pink", bins = 10) +
  labs(title = "Histogram of Cylinders vs. Weight",
       x = "Cylinders", y = "Weight") +
  theme_minimal()

# Boxplot of Weight across different numbers of cylinders
boxplot <- ggplot(mtcars, aes(x = factor(cyl), y = wt)) +
  geom_boxplot(fill = "brown") +
  labs(title = "Boxplot of Weight Across\nDifferent Numbers of Cylinders",
       x = "Cylinders", y = "Weight") +
  theme_minimal()

# Display both plots
grid.arrange(histogram, boxplot, ncol = 2)
```
